---
title: "hackbrazil1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# rough document with code snippets developed at infohackit 2016
# see the shiny folder for working app


### phylopic

```{r}
devtools::install_github("sckott/rphylopic")
library('rphylopic')


sp_names <- c("giant anteater",
              "blue macaw",
              "maned sloth",
              "wooly spider monkey",
              "golden lion tamerin",
              "golden toad")


tst <- name_search(text = "Homo sapiens")

phylo_rec <- name_search(text = "giant anteater")
img <- image_data(phylo_rec[1], size = 128)[[1]]




img <- image_data("27356f15-3cf8-47e8-ab41-71c6260b2724", size = "512")[[1]]

cat <- image_data("23cd6aa4-9587-4a2e-8e26-de42885004c9", size = 128)[[1]]
posx <- runif(50, 0, 1)
posy <- runif(50, 0, 1)
size <- runif(50, 0.01, 0.2)
plot(posx, posy, type = "n", main = "A cat herd")
for (i in 1:50) {
  add_phylopic_base(cat, posx[i], posy[i], size[i])
}






```



### brazil map
```{r}
library(rworldmap)
brazil_map <- getMap()[getMap()$ADMIN=="Brazil",]
sp::plot(brazil_map)

```


see this for more complicated version :
http://wallaceinitiative.org/


~ ggplot or base ? 3 circles overlapping
~ how would we specify the location and size of the circles
~ how would we get the size & location of the circle to change according to a param value ?
~ if I use ggplot then I could potentially use gganimate 
~ but if I do in ggplot then might be trickier to work out the overlap & plotting the map ?

~ May want to create the polygons first, if I want to calculate their overlaps ?
~ that would give me the flexibility to do on different shaped polygons later.


#simple base example


xs <- c(1,1.1,1.05) 
ys <- c(1,1,1.2)
radii <- c(0.01,0.01,0.01) #apart
#radii <- c(0.05,0.05,0.05) #2 together
#radii <- c(0.07,0.07,0.07) #3 together
radii <- c(0.15,0.15,0.15) #3 together

cols <- c(rgb(0,0,1,alpha=0.5),
          rgb(0,1,0,alpha=0.5),
          rgb(1,0,0,alpha=0.5) )

plot(0.5:1.5,0.5:1.5,type='n')
symbols(xs, ys, circles=radii, inches=FALSE, add=TRUE, fg=cols, bg=cols)          

#do i want to make it able to cope with different numbers of species ?

# I want to be able to capture the overlap of the polygons

# perhaps go back to plotting 3 polygons
# & using sp to calc the overlap of the 3 polygons
# then I have flexibility to change the polygons later
#I could maybe even plot the circles in ggplot ...


circle_fun <- function(center = c(0,0),r = 1, npoints = 100){
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}

#And a demonstration of it's use:

circ1 <- circle_fun(c(1,-1),1,npoints = 100)
#geom_path will do open circles, geom_polygon will do filled circles
#ggplot(dat,aes(x,y)) + geom_path()
ggplot(dat,aes(x,y)) + geom_polygon()

#I could make this into a circles_fun that returns columns of x,y & z
#but then would I be able to calculate the overlap ?
#I probably need to turn into sp objects to be able to use over ?

# from sp over vignette
xpol = c(0,1,1,0,0)
ypol = c(0,0,1,1,0)
pol = SpatialPolygons(list(
 Polygons(list(Polygon(cbind(xpol-1.05,ypol))), ID="x1"),
 Polygons(list(Polygon(cbind(xpol,ypol))), ID="x2"),
 Polygons(list(Polygon(cbind(xpol,ypol-1.05))), ID="x3"),
 Polygons(list(Polygon(cbind(xpol+1.05,ypol))), ID="x4"),
 Polygons(list(Polygon(cbind(xpol+.4, ypol+.1))), ID="x5")
 ))

pol = SpatialPolygons(list(
 Polygons(list(Polygon(cbind(xpol,ypol))), ID="x2"),
 Polygons(list(Polygon(cbind(xpol+0.5,ypol))), ID="x4"),
 Polygons(list(Polygon(cbind(xpol+.4, ypol+0.3))), ID="x5")
 ))
 

plot(pol)


library(rgeos)

#this works to get intersection
intersections <- gIntersection(pol[1], pol[2])


circles <- function(cx = c(1,1.1,1.05), cy = c(1,1,1.2), r = c(1,1,1), npoints = 100){

    polys <- data.frame(x = NULL, y = NULL, z = NULL)
    
    for(i in length(cx))
    {
     tt <- seq(0,2*pi,length.out = npoints)
     xx <- cx[i] + r[i] * cos(tt)
     yy <- cy[i] + r[i] * sin(tt) 
     
     poly <- data.frame(x = xx, y = yy, z = i)
     
     polys <- rbind( polys, poly )
    }

    
    return(polys)

}

circles <- function(cx = c(1,1.1,1.05), cy = c(1,1,1.2), r = c(1,1,1), npoints = 100){

    polys <- data.frame(x = NULL, y = NULL, z = NULL)
    
    for(i in length(cx))
    {
     tt <- seq(0,2*pi,length.out = npoints)
     xx <- cx[i] + r[i] * cos(tt)
     yy <- cy[i] + r[i] * sin(tt) 
     
     poly <- data.frame(x = xx, y = yy, z = i)
     
     polys <- rbind( polys, poly )
    }

    
    return(polys)

}



circle_fun <- function(center = c(0,0),r = 1, npoints = 100){
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}

circ1 <- circle_fun(center = c(1,1),r = 1)
circ1$z <- "c1"
circ2 <- circle_fun(center = c(1.1,1),r = 1)
circ2$z <- "c2"
circ3 <- circle_fun(center = c(1.05,1.2),r = 1)
circ3$z <- "c3"

circs <- rbind(circ1, circ2, circ3)

ggplot(circs, aes(x,y, fill = z)) + geom_polygon(alpha = 0.5)
#ggplot(circs,aes(x,y, colour=z)) + geom_path()

ggplot(circ1,aes(x,y, colour=z)) + geom_path()

## problem with the ggplot because circles are joined ...

#convert to sp object
pol1 <- Polygons(list(Polygon(circ1)), "c1")
pol2 <- Polygons(list(Polygon(circ2)), "c2")
pol3 <- Polygons(list(Polygon(circ3)), "c3")


pol = SpatialPolygons(list(pol1, pol2, pol3))

#polys <- SpatialPolygons(list(pol1, pol2, pol3))
sp::plot(polys, border='red')

sp::plot(pol, border='red')

#get intersection between 1 & 2
intersect1 <- gIntersection(pol[1], pol[2])
intersect2 <- gIntersection(intersect1, pol[3])

sp::plot(intersect2, border='green', fg='green', add=TRUE)


Text :
Global Warning
Addressing potential impacts of climate change on biodiversity in Brazil 

Climate change can move species distributions out of protected areas.


1. make the borders less ?
1. fix error of gIntersection ?


done 1. how to create circle polygon coords
done 1. how to plot circle
done 1. ggplot colour the circles
done 1. how to get overlap (might need to do 1 on 2 first, then the union of those 2 on 3)
done 1. how to put into shiny
done 1. add slider to set the radius
done 1. I may still want to do plotting in sp to keep easier ?

done 1. add checkboxes for range shift & range move
1. can I output the stats for % of each sp ?




