---
title: "hackbrazil1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### phylopic

```{r}
devtools::install_github("sckott/rphylopic")
library('rphylopic')


sp_names <- c("giant anteater",
              "blue macaw",
              "maned sloth",
              "wooly spider monkey",
              "golden lion tamerin",
              "golden toad")


tst <- name_search(text = "Homo sapiens")

phylo_rec <- name_search(text = "giant anteater")
img <- image_data(phylo_rec[1], size = 128)[[1]]




img <- image_data("27356f15-3cf8-47e8-ab41-71c6260b2724", size = "512")[[1]]

cat <- image_data("23cd6aa4-9587-4a2e-8e26-de42885004c9", size = 128)[[1]]
posx <- runif(50, 0, 1)
posy <- runif(50, 0, 1)
size <- runif(50, 0.01, 0.2)
plot(posx, posy, type = "n", main = "A cat herd")
for (i in 1:50) {
  add_phylopic_base(cat, posx[i], posy[i], size[i])
}






```



### brazil map
```{r}
library(rworldmap)


```


~ ggplot or base ? 3 circles overlapping
~ how would we specify the location and size of the circles
~ how would we get the size & location of the circle to change according to a param value ?
~ if I use ggplot then I could potentially use gganimate 
~ but if I do in ggplot then might be trickier to work out the overlap & plotting the map ?

~ May want to create the polygons first, if I want to calculate their overlaps ?
~ that would give me the flexibility to do on different shaped polygons later.


#simple base example


xs <- c(1,1.1,1.05) 
ys <- c(1,1,1.2)
radii <- c(0.01,0.01,0.01) #apart
#radii <- c(0.05,0.05,0.05) #2 together
#radii <- c(0.07,0.07,0.07) #3 together
radii <- c(0.15,0.15,0.15) #3 together

cols <- c(rgb(0,0,1,alpha=0.5),
          rgb(0,1,0,alpha=0.5),
          rgb(1,0,0,alpha=0.5) )

plot(0.5:1.5,0.5:1.5,type='n')
symbols(xs, ys, circles=radii, inches=FALSE, add=TRUE, fg=cols, bg=cols)          




